---
title: "R Notebook"
output: html_notebook
---
Loading libraries
```{r}
library(ggplot2)
library(randomForest)
library(doSNOW)
library(rpart)
library(rpart.plot)
library(caret)
library(aod)
```

Reading files
```{r}
train <- read.csv("train.csv")
test <- read.csv("test.csv")
class(train)
```

Let's look at fatures

We'll Start with Response
```{r}
train$Response <- as.factor(train$Response)
table(train$Response)
```

1. id -> remove

2.Gender
```{r}


#train.mod$Gender <- as.factor(train$Gender)
summary(train$Gender)
```
```{r}
ggplot(train, aes(Gender, fill = Response)) +
  geom_bar() +
  ggtitle("Respose by Gender") +
  xlab("Gender") +
  ylab("Response count")
```
We'll keep track of featue engineered dat frame in train.mod
```{r}
train.mod <- as.data.frame(train[,"Gender"])
names(train.mod)[1] <- "Gender"
```
3. Age
```{r}
summary(train$Age)
ggplot(train, aes(Age, fill = Response)) +
  geom_histogram() +
  ggtitle("Response by Age groups") +
  xlab("Age") +
  ylab("Response coubt")
```

```{r}
train.mod$Age <- as.numeric(train$Age)
```
4. Driving License
```{r}
ggplot(train, aes(Driving_License, fill = Response)) +
  geom_bar() +
  ggtitle("Respose by Driving License") +
  xlab("Driving License") +
  ylab("Response count")
```

```{r}
table(train$Driving_License, train$Response)
train.mod$Driving_License <- train$Driving_License
```

5. Region Codes
```{r}
length(unique(train$Region_Code))
summary(as.factor(train$Region_Code))
```
Region codes are important but, we can't use it as factors because
it has too many levels and using them as 'integers' loses their
quality.
So, we will make three columns for Region codes
One for 0 to 19
ne for 20 to 39
One for 40 to 52

```{r}
train$Region_Code <- as.integer(train$Region_Code)
Region_Code_1 <- as.integer(train$Region_Code)
Region_Code_2 <- as.integer(train$Region_Code)
Region_Code_3 <- as.integer(train$Region_Code)
for (i in 1:nrow(train)) {
  if(train$Region_Code[i]>=0 && train$Region_Code[i] <= 19) {
    Region_Code_2[i]<- -1
    Region_Code_3[i]<- -1
  }
  if(train$Region_Code[i] >= 20 && train$Region_Code[i] <= 39) {
    Region_Code_1[i]<- -1
    Region_Code_3[i]<- -1
  }
  if(train$Region_Code[i] >= 40 && train$Region_Code[i] <= 52) {
    Region_Code_1[i]<- -1
    Region_Code_2[i]<- -1
  }
}
```

```{r}
train.mod <- cbind(train.mod, Region_Code_1, Region_Code_2, Region_Code_3)
```


5. Previosly insured
```{r}
str(as.factor(train$Previously_Insured))
train.mod$Previously_Insured <- as.factor(train$Previously_Insured)
```
```{r}
ggplot(train, aes(Previously_Insured, fill = Response)) +
  geom_bar() +
  ggtitle("Respose vs Previosly insured") +
  xlab("Previos insured or not") +
  ylab("Respose count")
```

7. Vehicle Age

```{r}
str(as.factor(train$Vehicle_Age))
unique((train$Vehicle_Age))
```
```{r}
train.mod$Vehicle_Age <- as.factor(train$Vehicle_Age)
```
```{r}
ggplot(train, aes(as.factor(Vehicle_Age), fill = Response)) +
  geom_bar() +
  ggtitle("Respose count by Vehicle age") +
  xlab("Vehicle Age") +
  ylab("Response count")
```


8. Vehicle damage
```{r}
str(as.factor(train$Vehicle_Damage))
```
```{r}
ggplot(train, aes(Vehicle_Damage, fill = Response)) +
  geom_bar() +
  ggtitle("Respose by Vehicle_Damage") +
  xlab("Vehicle_Damage") +
  ylab("Response count")
```

```{r}
train.mod$Vehicle_Damage <- as.factor(train$Vehicle_Damage)
```


9. Annual Premium
```{r}
summary((train$Annual_Premium))
```
```{r}
ggplot(train, aes(x = Annual_Premium, fill = Response)) +
  geom_histogram(binwidth = 10000) +
  ggtitle("Response by Annual Premium of insurance") +
  xlab("Annual Premium") +
  ylab("Response count")
```

// Will think about it

10. Policy sales channel
```{r}
#policy.summary <-(summary(as.factor(train$Policy_Sales_Channel)))
(str(as.factor(train$Policy_Sales_Channel)))
```

```{r}
Policy_Sales_Channel.unique <- unique(train$Policy_Sales_Channel)
channelCap <- 550
a <- 2
Policy_Sales_Channel.unique.mod <- as.numeric()
for (i in 1:length(Policy_Sales_Channel.unique)) {
  ifelse(length(which(train$Policy_Sales_Channel == Policy_Sales_Channel.unique[i])) <=channelCap,
         Policy_Sales_Channel.unique.mod <- c(Policy_Sales_Channel.unique.mod, Policy_Sales_Channel.unique[i]),
         a <- 3)
}
length(Policy_Sales_Channel.unique.mod)
```

Policy_Sales_Channel.unique.mod have too less values, we'll make them zero

```{r}
Policy_Sales_Channel.mod <- train$Policy_Sales_Channel
for (i in 1:nrow(train)) {
  if(Policy_Sales_Channel.mod[i] %in% Policy_Sales_Channel.unique.mod) {
    Policy_Sales_Channel.mod[i] = -1
  }
}
length(unique(Policy_Sales_Channel.mod))
```

Perfect!
Now add this to train.mod
```{r}
train.mod$Policy_Sales_Channel <- Policy_Sales_Channel.mod
```



11. Vintage
```{r}
summary((train$Vintage))
```
Add to train mod
```{r}
train.mod$Vintage <- train$Vintage
```







Try random forest

```{r}

start.time = Sys.time()
total.time <- Sys.time()

cluster1 <- makeCluster(3, type = "SOCK")
registerDoSNOW(cluster1)


set.seed(1234)
rf.1 <- randomForest(x = train.mod, y = as.factor(train$Response), importance = TRUE, ntree = 400)
rf.1
varImpPlot(rf.1)


stopCluster(cluster1)

total.time <- Sys.time() - start.time
total.time



```



```{r}
train.mod.1 <- as.data.frame(subset(train, select = c(Previously_Insured)))
str(train.mod.1)
```




```{r}

start.time = Sys.time()
total.time <- Sys.time()

cluster1 <- makeCluster(3, type = "SOCK")
registerDoSNOW(cluster1)


set.seed(1234)
rf.1 <- randomForest(x = train.mod.1, y = as.factor(train$Response), importance = TRUE, ntree = 50)
rf.1
varImpPlot(rf.1)


stopCluster(cluster1)

total.time <- Sys.time() - start.time
total.time



```










```{r}
cv.folds.10 <- createMultiFolds(train$Response, k=10, times = 10)

cntrlFunction <- trainControl(method = "repeatedcv", number = 3,
                             repeats = 3, index = cv.folds.10)

start.time = Sys.time()
total.time <- Sys.time()

cluster1 <- makeCluster(3, type = "SOCK")
registerDoSNOW(cluster1)


set.seed(1234)


rpart.cv <- train(x = train.mod, y = train$Response, method = "rpart",
                  tunelength=10, trControl=cntrlFunction)


rpart.cv
stopCluster(cluster1)

total.time <- Sys.time() - start.time
total.time

```



```{r}
rpart.model <- rpart(train$Response ~ train.mod)
rpart.model
```


```{r}
train.mod$Response <- as.factor(train$Response)
```
```{r}
logRegModel <- glm(Response ~ . , data = train.mod , family = "binomial")
summary(logRegModel)
```

















